---
title: "Cross_Validation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mgcv)
library(modelr)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


generate a dataset

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()

```

Training and testing


```{r}
train_df = sample_frac(nonlin_df, size = .8)
  test_df = anti_join(nonlin_df, train_df, by = "id")

  ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")

  
```

fit three models of varying goodness 
```{r}
linear_mod = lm( y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```
 
 let's look at some fits.
 
```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) +
    geom_point() + 
   geom_line(aes(y = pred), color = "red")
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
    geom_point() + 
   geom_line(aes(y = pred), color = "red")
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
    geom_point() + 
   geom_line(aes(y = pred), color = "red")
  
```


```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

testing data is involved when we see which model is better. 
0.3 is better than 0.8. 

if train_df replace test_df, value for train is lower than test. the size is larger and standard error will decreaase. 

## do this all using `modelr`

```{r}
cv_df =
  crossv_mc(nonlin_df, 100)
```

one note about resample

```{r}
cv_df %>% pull(train) %>% .[[3]] %>% as_tibble
```

transfer to data frame.

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

try to fitting the linear model to all of these.

```{r}
cv_results = 
cv_df %>% 
  mutate(
    linear_mods = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mods = map(.x = train, ~gam(y ~ s(x), data = .x)),
    wiggly_mod = map(.x = train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x)),
    rmse_lin = map2_dbl(.x = linear_mods, .y = test, ~rmse(.x,.y)),
    rmse_smo = map2_dbl(.x = smooth_mods, .y = test, ~rmse (.x,.y)),
     rmse_wig = map2_dbl(wiggly_mod, test, ~rmse (model = .x,data = .y))
  ) 
  
```


map2, has two column. 

```{r}
cv_results %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
smooth model is the best!!!!!  


## child growth


```{r}
child_growth = read_csv("./nepalese_children.csv")

```


```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point()

child_growth =
  child_growth %>% 
  mutate(weight_cp = (weight > 7) * (weight - 7))
```

add change point term


```{r}
linear_mod    = lm(armc ~ weight, data = child_growth)
pwl_mod    = lm(armc ~ weight + weight_cp, data = child_growth)
smooth_mod = gam(armc ~ s(weight), data = child_growth)
```


```{r}
 cv_df =
  crossv_mc(child_growth, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

```

```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(armc ~ weight, data = .x)),
         pwl_mod     = map(train, ~lm(armc ~ weight + weight_cp, data = .x)),
         smooth_mod  = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_pwl    = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)))
```


```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()

```















